The Actions We Compute are Not Invariant

### 2018-12-03 paper/ms.tex
Update paper

\title{Actions Computed in the Milky Way are Not Invariant}

@@

\section{Simulations}

>>>>

\title{The Actions We Compute are Not Invariant}

@@

\section{Optimally Axisymmetric Frame}
An analytic, axisymmetric potential with a known reference frame is a far too
simple description of the Milky Way. We thus turn to cosmological zoom-in
simulations as approximations to a ``true'' Milky Way potential. It is important to remember that

\subsection{Cosmological Zoom-in} \label{ssec:cosmozoom}
Cosmological zoom-ins allow one to simulate a selected region at high resolution embedded in a low-resolution cosmological background \citep[e.g.][]{1993ApJ...412..455K,2014MNRAS.437.1894O}

\subsection{Cluster Simulations} \label{ssec:cluster_sim}
